\documentclass{contest-set}

\title{Holiday Contest}
\motto{``The proof is trivial, and is left as an exercise.''}
\subheader{SLSS Computer Science Club}
\date{December 14, 2018}
\institute{Stephen Lewis Secondary School}
\organization{Computer Science Club}

\begin{document}
\maketitle

\section{Communist Poker Game}
The committee organising a holiday poker game has decided that in order to promote equity and diversity, the poker game will run under communist rules.

At the end of the game, the committee wants to balance the payout of each player by minimising debt; that is, they want to get all players out of debt. They will do this by connecting the players into a network and then moving money from player to player by a sequence of moves until everyone is out of debt. A move consists of selecting a player $p$ and then moving one dollar across each edge adjacent to $p$. 

Given a network of players, determine the minimum number of moves needed to get all players out of debt.

\inputformat
The first line of input contains two space-separated integers $n$ and $k$ describing the number of players and the number of connections respectively. The next $n$ lines contain a single space-separated integer describing the amount of money that the $i$-th player ($1 \leq i \leq n$) has. The next $k$ lines contain two space-separated integers $i$ and $j$ denoting that player $i$ is connected to $j$ in the network.

\outputformat
The output consists of a single space-separated integer denoting the minimum number of moves that are needed to balance the network. If it is impossible, output $-1$.

\end{document}